Gametic Selection, Meiotic Drive, Sex Ratio Bias, and Transitions Between Sex Determination Systems

### 2017-05-24 LaTeX/Turnover.tex
small chagnes to s.1 text

Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which is also where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2(a) in][]{Otto2014}.
The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.

>>>>

Figure \ref{fig:Region_Plots} shows where the sex-specialist (red) and perverse (blue) hypotheses are valid.
The left panel demonstrates that both hypotheses can be simultaneously valid with overdominance in both sexes and sex differences in selection, which overlaps the parameter region where there is selection for increased recombination between the sex chromosomes \citep[compare with figure 2a in][]{Otto2014}.
The right panel shows that the perverse hypothesis is no longer valid when selection is exactly the same in both sexes, despite the fact that there is selection for increased recombination between the sex chromosomes with sufficiently strong overdominance \citep[compare with figure 3 in][]{Otto2014}.
